Visualizing the Geography of Genetic Variants

### 2016-07-01 paper.Rmd
fixing more typos

Reference datasets for population genetic variation has greatly expanded since the release of the HGDP Illumina 650Y dataset @li2008worldwide that formed the basis of the HGDP Selection Browser maps.  The most notable advance is the publication of the 1000 Genomes phase 3 data @10002015global though additional datasets are coming online @meyer2012high, @lazaridis2014ancient.

@@

```{r figure1, echo=FALSE, message=FALSE, fig.height=4, fig.width=4, fig.align='center', fig.cap='Schematic diagram of the Geography of Genetic Variants (GGV) browser. We compute minor allele frequencies from publicly available population genetic datasets from the 1000 Genomes Project, Human Genome Diversity Project (HGDP) and Population Reference Sample (POPRES). These allele frequencies are stored in a SQL database along side with geographic coordinates associated with each population. The front-end visualization was created using d3 and accesses allele frequency and population meta-data from a REST API implemented in the python library flask.'}
img <- readPNG("figures/png/figure1.png")
grid.raster(img)
```

@@

```{r figure4, echo=FALSE, message=FALSE, fig.height=4, fig.width=5, fig.align='center', fig.cap='Example maps from the Geography of Genetic Variants browser displaying the use of frequency scales for more expressive representations of rare variation on geographic maps. The blue pie charts convey a give minor allele frequency out of 100 percent, the green out 1 percent, and the red out of .01 percent.'}
img <- readPNG("figures/png/figure4.png")
grid.raster(img)
```

@@

```{r figure5, echo=FALSE, message=FALSE, fig.height=4, fig.width=5, fig.align='center', fig.cap='Example maps from the Geography of Genetic Variants browser displaying the use of a force directed layout to limit visual clutter when many populations overlap in geographic position. The left map shows the original population locations while the right shows the application of the force directed layout.'}
img <- readPNG("figures/png/figure5.png")
grid.raster(img)
```

>>>>

Reference datasets for population genetic variation has greatly expanded since the release of the HGDP Illumina 650Y dataset @li2008worldwide that formed the basis of the HGDP Selection Browser maps.  The most notable advance is the publication of the 1000 Genomes Phase 3 data @10002015global though additional datasets are coming online @meyer2012high, @lazaridis2014ancient.

@@

```{r figure1, echo=FALSE, message=FALSE, fig.height=4, fig.width=4, fig.align='center', fig.cap='Schematic diagram of the Geography of Genetic Variants (GGV) browser. We compute minor allele frequencies from publicly available population genetic datasets from the 1000 Genomes Project, Human Genome Diversity Project (HGDP) and Population Reference Sample (POPRES). These allele frequencies are stored in a SQL database along side with geographic coordinates associated with each population. The front-end visualization was created using D3.js and accesses allele frequency and population meta-data from a REST API implemented in the python library flask.'}
img <- readPNG("figures/png/figure1.png")
grid.raster(img)
```

@@

```{r figure4, echo=FALSE, message=FALSE, fig.height=5, fig.width=5, fig.align='center', fig.cap='Example maps from the Geography of Genetic Variants browser displaying the use of frequency scales for more expressive representations of rare variation on geographic maps. The blue pie charts convey a give minor allele frequency out of 100 percent, the green out 1 percent, and the red out of .01 percent.'}
img <- readPNG("figures/png/figure4.png")
grid.raster(img)
```

@@

```{r figure5, echo=FALSE, message=FALSE, fig.height=6, fig.width=5, fig.align='center', fig.cap='Example maps from the Geography of Genetic Variants browser displaying the use of a force directed layout to limit visual clutter when many populations overlap in geographic position. The left map shows the original population locations while the right shows the application of the force directed layout.'}
img <- readPNG("figures/png/figure5.png")
grid.raster(img)
```

### 2016-07-01 paper.tex
fixing more typos

Reference datasets for population genetic variation has greatly expanded
since the release of the HGDP Illumina 650Y dataset {[}16{]} that formed
the basis of the HGDP Selection Browser maps. The most notable advance
is the publication of the 1000 Genomes phase 3 data {[}17{]} though
additional datasets are coming online {[}18{]}, {[}19{]}.

>>>>

Reference datasets for population genetic variation has greatly expanded
since the release of the HGDP Illumina 650Y dataset {[}16{]} that formed
the basis of the HGDP Selection Browser maps. The most notable advance
is the publication of the 1000 Genomes Phase 3 data {[}17{]} though
additional datasets are coming online {[}18{]}, {[}19{]}.
